### 2022-09-03 main/chapter_searches.tex
some rearrangements

% p-values
(probable error?), known in modern jargon as $p$-values

% estimators --- not unbiased!

% savage likelihood principle

\TODO{Fisher's great contribution --- likelihood}
\TODO{
Fisher:
criteria for estimators,
(consistency, efficiency, sufficiency)
~\cite{fisher1922estimators}
testing, p-value,
likelihood, also ratios of p-values (here named probable errors)
(introduced the term likelihood? cite?)
~\cite{fisher1921probable}
tail area = significance
~\cite{fisher1925smrw}
}

@@

% TODO Kolmogorov axioms, unbiasedness
\TODO{
Given all this understanding, what I do not understand is their choice to
convert this to a $p$-value.
Seems to be this idea of long-run correctness guarantees.
But their derivation does rely on long-run frequencies.
}

@@

\TODO{
tossing a coin is considered random
but if instead you are presented with a coin hidden under a cloth,
no frequency interpretation --- it either is or is not heads
you are therefore denied the ability to make uncertain predictions.
more generally, you are not allowed to express an uncertainty in something
unless some random process is involved
}

\TODO{
Can keep likelihoods, but cannot compute evidence values unless the prior
has a frequency interpretation.
}

@@

\TODO{
maximum likelihood, p-values, confidence intervals, and biasedness of
estimators.
}

\TODO{
Lehmann~\cite{lehmann2005testing};
p. 26 poisson inadmissable example;
L-unbiased with given loss function;
}

\TODO{maximum likelihood}
\TODO{p-value}
\TODO{p-value:
The chance of a small $p$-value is small.
This is true, but not interesting because the value of any $p$-value is small.
By construction $p$-values are uniformly distributed on the unit interval
under a given hypothesis.
The frequency of $p < 0.05$ is $5\%$, but so also is the frequency of
$0.6 < p < 0.65$.
The frequency of $p < \varepsilon$ is identical to the frequency
of $0.6 < p < 0.6 + \varepsilon$.
An appropriate choice of test statistic is therefore necessary for the
$p$-value to have meaning.
}
Figure~\ref{fig:searches_significant}
\TODO{confidence interval}
\TODO{unbiased}

>>>>

% p-values
\TODO[
(probable error?), known in modern jargon as $p$-values
tail area = significance
~\cite{fisher1925smrw}
}

\TODO{maximum likelihood}
\TODO{p-value}
\TODO{p-value:
The chance of a small $p$-value is small.
This is true, but not interesting because the value of any $p$-value is small.
By construction $p$-values are uniformly distributed on the unit interval
under a given hypothesis.
The frequency of $p < 0.05$ is $5\%$, but so also is the frequency of
$0.6 < p < 0.65$.
The frequency of $p < \varepsilon$ is identical to the frequency
of $0.6 < p < 0.6 + \varepsilon$.
An appropriate choice of test statistic is therefore necessary for the
$p$-value to have meaning.
}
Figure~\ref{fig:searches_significant}

% estimators --- not unbiased!
\TODO{
(unbiased estimators)
Lehmann~\cite{lehmann2005testing};
p. 26 poisson inadmissable example;
L-unbiased with given loss function;
}

% savage likelihood principle
\TODO{
Fisher:
criteria for estimators,
(consistency, efficiency, sufficiency)
~\cite{fisher1922estimators}
}

@@

\TODO{
Given all this understanding, what I do not understand is their choice to
convert this to a $p$-value.
Seems to be this idea of long-run correctness guarantees.
But their derivation does rely on long-run frequencies.
}

@@

@@

\TODO{
maximum likelihood, p-values, confidence intervals
}

\TODO{confidence interval}
\TODO{unbiased}
